Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-21 ICML-submission/introduction.tex
Update introduction.tex
Fixed a bad reference (coming from merging the two separability definitions)

In this paper, we focus on the special case when the examples chosen by the
adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
two notions of linear separability, \emph{weak} and \emph{strong}, formally
stated in
Definitions~\ref{definition:weak-linear-separability}~and~\ref{definition:strong-linear-separability}.
The standard notion of multiclass linear
separability~\citep{Crammer-Singer-2003} corresponds to the weak linear
separability. For binary classification, the weak and strong separability are
identical. However, they differ for multiclass classification with $K \ge 3$
classes. For multiclass classification with $K$ classes, weak linear
separability means that the examples from each class lie in an intersection of
$K-1$ halfspaces and the examples outside of the class lie in the complement of
the intersection of the halfspaces. Strong linear separability means that
examples from each class are separated from the remaining examples by a
\emph{single} hyperplane.

>>>>

In this paper, we focus on the special case when the examples chosen by the
adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
two notions of linear separability, \emph{weak} and \emph{strong}, formally
stated in
Definition~\ref{definition:weak-linear-separability}.
The standard notion of multiclass linear
separability~\citep{Crammer-Singer-2003} corresponds to the weak linear
separability. For binary classification, the weak and strong separability are
identical. However, they differ for multiclass classification with $K \ge 3$
classes. For multiclass classification with $K$ classes, weak linear
separability means that the examples from each class lie in an intersection of
$K-1$ halfspaces and the examples outside of the class lie in the complement of
the intersection of the halfspaces. Strong linear separability means that
examples from each class are separated from the remaining examples by a
\emph{single} hyperplane.
